Quantizing the Bosonic String on a Loop Quantum Gravity Background

### 2023-11-21 lqg-strings.tex
Reduced the EoM into a Klein-Gordon equation and added a section relating it to sec(3)

As for the embbeding fields equation, we get a wave equation for the coupled metric
\begin{equation} \label{eqn:variation-wrt-X}
	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:bimetric-wave-equation}
	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
\end{equation}
where
\begin{equation} \label{eqn:coupled-ws-metric}
	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
\end{equation}
\begin{equation} \label{eqn:combined-bulk-metric}
	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
\end{equation}
in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$. Since 2D metrics can always be written as a conformal metric, it is easy to see that eq(\ref{eqn:coupled-ws-metric}) can be recast as
\begin{equation} \label{eqn:conformal-coupled-metric}
	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} ,
\end{equation}
and in the special case of the second metric coming from the quantum geometry inverse area correction where $T' = T g \Delta / 2$, we see that eq(\ref{eqn:bimetric-wave-equation}) trivially reduces to eq(\ref{eqn:simplified-modified-wave-eqn}) found before when the background metric $F_{\mu \nu} = 2 G_{\mu \nu}$ is fixed i.e $\partial _{\lambda} F_{\mu \nu} = 0$.

>>>>

As for the embbeding fields equation, we get a wave equation for the coupled metric
\begin{equation} \label{eqn:variation-wrt-X}
	\frac{\delta S_{P B}}{\delta X^{\lambda}} \overset{!}{=} 0
\end{equation}
\begin{equation*}
	\downarrow
\end{equation*}
\begin{equation} \label{eqn:bimetric-wave-equation}
	f^{\prime a b} \partial _{a} \partial _{b} X^{\mu} F_{\mu \lambda} = \frac{1}{2} f^{\prime a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} \frac{\partial F_{\mu \nu}}{\partial X^{\lambda}} ,
\end{equation}
where
\begin{equation} \label{eqn:coupled-ws-metric}
	f^{\prime a b} & = T \sqrt{- g} g^{a b} + T' \sqrt{- h} h^{a b}
\end{equation}
\begin{equation} \label{eqn:combined-bulk-metric}
	F_{\mu \nu}    & = G_{\mu \nu} + H_{\mu \nu} ,
\end{equation}
in which we add a prime in the coupled metric $f^{\prime a b}$ since it is not quite the metric induced by the combined bulk metric $F_{\mu \nu}$. Since 2D metrics can always be written as a conformal metric, it is easy to see that eq(\ref{eqn:coupled-ws-metric}) can be recast as
\begin{equation} \label{eqn:conformal-coupled-metric}
	f^{\prime a b} = T \eta ^{a b} + T' \eta ^{a b} = (T + T') \eta ^{a b} .
\end{equation}
In the special case where the second metric comes from the quantum geometry correction in the form of inverse area, where $T' = T k \Delta / 2$, eq(\ref{eqn:bimetric-wave-equation}) thus reduces to
\begin{equation} \label{eqn:reduced-Polyakov-equation}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\kappa} = \frac{1}{2} \eta ^{a b} \partial _{a} X^{\mu} \partial _{b} X^{\nu} F^{\kappa \lambda} \partial _{\lambda} F_{\mu \nu} ,
\end{equation}
where if the R.H.S is set to be proportional to the embbeding fields, we thus get a Klein-Gordon equation
\begin{equation} \label{eqn:Polyakov-Klein-Gordon-equation}
	\eta ^{a b} \partial _{a} \partial _{b} X^{\mu} - \kappa X^{\mu} = 0 .
\end{equation}

\subsection{Relation With The Nambu-Goto Equation}

At first glance, our recent analysis seems to conflict with the one done in sec(\ref{sec:modified-eom}), but as pointed out in \cite{}, the variable-speed wave equation can be turned into a Klein-Gordon equation as long as the speed function satisfies certain constraints [need to show], while it is known from the GR literature that variable-speed waves are equivalent to waves in curved space, which is precisely what we found, since for eq(\ref{eqn:bimetric-wave-equation}) to reduce into the Klein-Gordon equation(\ref{eqn:Polyakov-Klein-Gordon-equation}) we needed for the background geometry to be dynamical.
